Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2023-10-26 README.Rmd
add README files

```{r}
proj_history <-
  gert::git_tag_list() |>
  dplyr::rename(
    milestone = name,
    milestone_hash = commit) |>
  mutate(
    commit_hash = (\(x) purrr::pmap_chr(list(milestone, ref, milestone_hash), .f = function(milestone, ref, milestone_hash) {
      gert::git_commit_info(milestone_hash)$id
    }))()
  ) |>
  left_join(
    gert::git_log() |>
      rename(commit_hash = commit)
  ) |>
  mutate(
    milestone_link = paste0(get_git_url(), '/releases/tag/', milestone),
    link = commit_hash,
    commit_link = paste0(get_git_url(), '/tree/', commit_hash)
  ) |> 
  separate(message, into = c("message", "code"), sep = "code") |> 
  mutate(
    code = str_replace_all(code, "\\|\\>", "\\|\\>\\\n"),
    message = str_remove(message, "\\\nobject_hash.*$")
  )

>>>>

```{r}
proj_history <-
  gert::git_tag_list() |>
  dplyr::rename(
    milestone = name,
    milestone_hash = commit) |>
  mutate(
    commit_hash = (\(x) purrr::pmap_chr(list(milestone, ref, milestone_hash), .f = function(milestone, ref, milestone_hash) {
      gert::git_commit_info(milestone_hash)$id
    }))()
  ) |>
  left_join(
    gert::git_log() |>
      rename(commit_hash = commit)
  ) |>
  mutate(
    milestone_link = paste0(get_git_url(), '/releases/tag/', milestone),
    link = commit_hash,
    commit_link = paste0(get_git_url(), '/tree/', commit_hash)
  ) |> 
  separate(message, into = c("message", "code"), sep = "code") |> 
  mutate(
    code = str_replace_all(code, "\\|\\>", "\\|\\>\\\n"),
    message = str_remove(message, "\\\nobject_hash.*$"),
    milestone = str_c("[", milestone, "]", "(www.google.com)")
  )
